The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-12 paper/ms.tex
paper minor update

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every nearby star cluster in
  the Galaxy.
  % Aims
  As part of the CDIPS project, we have begun processing the TESS
  full-frame images to make high-precision light curves for candidate
  members of stellar associations, moving groups, and open clusters.
  %
  Our eventual hope is to discover giant transiting planets, and probe
  the exoplanet size and separation distributions for planets younger
  than 1 Gyr.
  %
  For this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve repesents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and light curve
  processing techniques we used to create the light curves, which
  have noise properties in-line with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates identified from
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the need for additional
  spectroscopic and photometric observations.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The data products include both the light curves and also vetting
  reports, all of which are available at
  \url{archive.stsci.edu/prepds/cdips}.
\end{abstract}

@@

A major motivator for the CDIPS project is to increase the number of
cluster stars for which continuous photometric timeseries are
available, and thus facilitate studies of exoplanetary and stellar
processes across different times and stellar environments.
An essential aspect of the project is therefore to define a {\it
cluster star sample}, made of stars that are thought to be
members of clusters.

Performing a homogeneous membership determination for every known
cluster is beyond the scope of the current work.  Instead, we collect
various cluster membership catalogs from the literature.  We then use
them to identify cluster members within the TESS images.  In initially
selecting stars, we aim for completeness, not accuracy.  If there has
been a claim in the literature that a star should be considered a
cluster member, we would like to report a light curve for the star.
For stars that are photometrically interesting, we can perform post-hoc
cluster membership quality checks using Gaia DR2 astrometry and photometry.

Table~N describes the cluster membership catalogs we have used to
identify candidate cluster members.  Since our photometric reduction
is based on positions reported in {\it Gaia DR2}, each of our
light curve sources by default is associated with a Gaia identifier.
Correspondingly, the cluster membership determinations performed by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
easiest case for us to merge against our light curve database.
For the TESS Sectors 1--5 light curves produced in this study, this
yielded X and Y light curves respectively.

@@

\paragraph{{\it Gaia}-derived OC memberships}
At the time of writing, two relatively large, homogeneous cluster
memberships studies had been performed using {\it Gaia}-DR2: those by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.

@@

@@

\subsection{Summary of selected stars}

>>>>

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has started to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  As part of the CDIPS project, we have been processing the TESS
  full-frame images to make high-precision light curves stars that
  could be members of stellar associations, moving groups, and open clusters.
  %
  Our eventual hope is to discover giant transiting planets, and probe
  the exoplanet size and separation distributions for planets younger
  than 1 Gyr.
  %
  For this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties in agreement with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the value that additional
  spectroscopic, photometric, and imaging observations will have in
  verify that these candidates are in fact planets.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting are available at
  \url{archive.stsci.edu/prepds/cdips}.
\end{abstract}

@@

A major aim of the CDIPS project is to increase the number of
cluster stars for which photometric time-series are
available, to facilitate studies of exoplanetary and stellar
processes across different times and stellar environments.
An essential step is therefore to define a sample of
stars that are thought to be young, or members or clusters, or both.

However, a homogeneous membership calculation for every known
cluster is outside our scope.  So too is a homogeneous search for
young stars across the galaxy.
Instead, we opt to collect
and concatenate appropriate catalogs from across the literature.  
We then use the resulting meta-catalog to identify our target stars within the 
TESS images.

In our initial stellar selection our aim is therefore completeness, not 
accuracy.  If there has
been a claim in the literature that a star should be considered a
cluster member, or a young star, we would like to report a light curve for the 
star.
For stars that are photometrically interesting, we can perform post-hoc
quality checks using Gaia DR2 astrometry and photometry to assess cluster 
membership and youth.

\S~\ref{subsec:oc} describes the large catalogs we used to 
identify candidate members of open clusters.
\S~\ref{subsec:mg} describes the smaller catalogs we used to identify 
candidate members of moving groups, stellar associations, as well as young 
stars identified through combined Gaia photometry and astrometry.
\S~\ref{subsec:ocmgsummary} then reports summary statistics for the entire 
sample of about one million target stars.

@@

At the time of writing, two relatively large, homogeneous cluster
memberships studies had been performed using {\it Gaia}-DR2: those by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
There were also two large membership studies based on proper motion and 
photometric catalogs that were of interest: the studies of
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.

\paragraph{{\it Gaia}-derived OC memberships}

@@

In our photometric reduction,  our default identifier for all sources
is the Gaia DR2 \texttt{source\_id}.
The TIC identifiers are found through a spatial cross-match after the light 
curves have been made
\citep{stassun_TIC_2018,stassun_TIC8_2019}
This is because Gaia DR2 is the base-catalog used to project
sources from celestial coordinates to the imaging plane (\S~\ref{sec:method}).
It also has the advantage that for any Gaia-derived cluster memberships, 
we preform cross-matching directly via the source identifiers.

@@

\subsection{Summary of selected stars}
\label{subsec:ocmgsummary}
